---
title: "Setting Up Folders"
author: "Keith Baggerly"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Setting Up Folders}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

For me, setting up a new analysis project begins with 
defining a consistently named set of folders so I'll
know where everything goes. Invoking

```{r populate, eval=FALSE}

populate_project()

```

creates a set of folders at the top level of the 
project (where the .Rproj file resides). By default,
it will create 

```
R/
data/
results/
```

and nothing else, because that's my preferred setup. 

If you have an alternate setup you'd prefer, 
you can supply a vector with your own names, e.g.

```{r populate_w_input, eval=FALSE}

populate_project(folder_names = c("Rmd", "data", "reports"))

```

creates

```
Rmd/
data/
reports/
```

My goal in automating this step is to increase the odds
that I'll use the same setup consistently over time. 

I prefer a fairly minimalist setup with a small number
of folders myself. Other suggestions can be found at
[Project Template](http://projecttemplate.net/), or in the 
[Good Enough Guidelines](https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005510) from _PLoS Computational Biology_.

I use `data/` for raw source data and metadata, ideally downloaded
from a commonly accessible repository. The goal is to treat all 
files in this folder as "read-only" and script all interactions
with them. 

I use `R/` for my various analysis Rmd and R files, which 
I number sequentially, e.g. "01_gather_raw_data.R", 
"02_parse_dataset_1.Rmd". I bundle both types of files
here because `rmarkdown::render()` can generate markdown
(md) files from either. I may also include a small file
of `helper_functions.R`. If I have more than one or two
analysis scripts (unnumbered .R files), I'll try to create
a separate package for them.

I use `results/` to store all output generated by the analyses
in `R/`, including processed data. Everything in `results/`
should be derived from files in `R/` and `data/`.



